Image projections along an axe

### 2006-01-30 article/Article.tex
add an example of implementation
darcs-hash:20060130210118-2fc9d-ba76003c9207a5292831ba53f2e0ffe3464ee5ba.gz

@@

\section{Conclusion}
The new classes give more feature and more flexibility with equivalent
performance than the current available filter, but loss the compatibility with
the previous filter. I propose to mark AccumulateImageFilter as deprecated in
the next release of ITK to incite user to the new class.

>>>>

\section{Implemeting a new projection method}
As an example, here is a filter which implement a square sum projection along a
axe. This example may be useful in case of signed input type.

Everything can be done in a single file, itkSquareSumProjectionImageFilter.h.
\small \begin{verbatim}
#ifndef __itkSquareSumProjectionImageFilter_h
#define __itkSquareSumProjectionImageFilter_h
\end{verbatim} \normalsize
The itkProjectionImageFilter.h header must be included.
\small \begin{verbatim}
#include "itkProjectionImageFilter.h"
#include "itkNumericTraits.h"

namespace itk {

namespace Function {
\end{verbatim} \normalsize
Now, create the class which do the real work: receive all the pixel values and
give the result at the end. The class is created in the itk::Function names pace
to avoid putting to much things in itk name space, and is templated over the
type of the input and the output pixel.
On object of this class is created for each pixel in the output image.
\small \begin{verbatim}
template <class TInputPixel, class TOuputPixel>
class SquareSumAccumulator
{
public:
\end{verbatim} \normalsize
The constructor must take one parameter: the number of pixels to accumulate
during the projection. In that case, this parameter is not useful, so it is not
saved in an attribute of the class. The sum is initialized to zero.

The destructor is empty - there is nothing to do.
\small \begin{verbatim}
  SquareSumAccumulator( unsigned long nb )
    {
    m_SquareSum = NumericTraits< TOuputPixel >::Zero;
    }
  ~SquareSumAccumulator(){}
\end{verbatim} \normalsize
The operator() is called for each pixel. In this method, the square sum is
contructed, pixel after pixel. The method is declared inline for best
performance.
\small \begin{verbatim}
  inline TInputPixel operator()( const TInputPixel &input )
    {
    m_SquareSum = m_SquareSum + ( input * input );
    }
\end{verbatim} \normalsize
GetValue() is called to set the value of the result image. In that example, the
sum is just return, but more complex computation can be done here (see the
MedianProjectionImageFilter for an example). ProjectionImageFilter cast the
output of this method to the output image's pixel type.
\small \begin{verbatim}
  inline TOuputPixel GetValue()
    {
    return m_SquareSum;
    }
\end{verbatim} \normalsize
The internal attribute which accumulate the square sum.
\small \begin{verbatim}
  TOuputPixel m_SquareSum;
};
} // end namespace Function
\end{verbatim} \normalsize
The class is declared. It inherits from ProjectionImageFilter, and declares the
usual types and methods.
\small \begin{verbatim}
template <class TInputImage, class TOutputImage>
class ITK_EXPORT SquareSumProjectionImageFilter :
    public
    ProjectionImageFilter<TInputImage, TOutputImage,
      Function::SquareSumAccumulator< typename TInputImage::PixelType,
        typename TOutputImage::PixelType > >
{
public:
  typedef SquareSumProjectionImageFilter Self;
  typedef ProjectionImageFilter<TInputImage, TOutputImage, 
    Function::SquareSumAccumulator< typename TInputImage::PixelType,
      typename TOutputImage::PixelType > > Superclass;

  typedef SmartPointer<Self>   Pointer;
  typedef SmartPointer<const Self>  ConstPointer;

  /** Runtime information support. */
  itkTypeMacro(SquareSumProjectionImageFilter, ProjectionImageFilter);

  /** Method for creation through the object factory. */
  itkNewMacro(Self);

protected:
  SquareSumProjectionImageFilter() {}
  virtual ~SquareSumProjectionImageFilter() {}

private:
  SquareSumProjectionImageFilter(const Self&); //purposely not implemented
  void operator=(const Self&); //purposely not implemented

}; // end SquareSumProjectionImageFilter

} //end namespace itk
#endif
\end{verbatim} \normalsize
That's all.

@@

\section{Conclusion}
The new classes give more feature and more flexibility with equivalent
performance than the current available filter, but loss the compatibility with
the previous filter. I propose to mark AccumulateImageFilter as deprecated in
the next release of ITK to incite ITK user to use the new class.
